\newglossaryentry{Smalltalk}{name={Smalltalk},description={\emph{Smalltalk} is an object-oriented, reflective, dynamically typed, \textit{all is object} programming languages.}}

\newglossaryentry{primitive}{name={primitive},description={A \emph{primitive} is a C implemented method directly interpreted by the VM.}}

\newglossaryentry{Pharo}{name={Pharo},description={\emph{Pharo} is a fork of Squeak, an implementation of the object-oriented, dynamically typed, reflective programming language Smalltalk.}}

\newglossaryentry{Special Objects Array}{name={Special Objects Array},description={The \emph{Special Objects Array} is an array shared by the image and the VM which store primordial information.}}

\newglossaryentry{Garbage Collector}{name={Garbage Collector},description={The \emph{Garbage Collector} is a mechanism which consist in automatically destroy unreferenced objects of a living system in order to recover memory.}}

\newglossaryentry{Micro Squeak}{name={Micro Squeak},description={\emph{Micro Squeak} is a \emph{John Maloney}'s project which produces a headless 57k image with a few basic classes as a proof of concept.}}

\newglossaryentry{Moose}{name={Moose},description={\emph{Moose}  is a platform for software and data analysis maintained by a part of the RMoD team.}}

\newglossaryentry{SVN}{name={SVN},description={\emph{Subversion} is a tool for version control.}}


                 
% ------------------------------------------------------------------------ 	%
%											%
%				     Acronyms					%
%											%
% ------------------------------------------------------------------------ 	%

\newacronym[\glsshortpluralkey=VM,\glslongpluralkey=Virtual Machine]{VM}{VM}{Virtual Machine}

\newacronym[\glsshortpluralkey=INRIA,\glslongpluralkey=INRIA]{INRIA}{INRIA}{Institut National de Recherche en Informatique et en Automatique}

\newacronym[\glsshortpluralkey= IDE,\glslongpluralkey= IDE]{IDE}{IDE}{Integrated Development Environment}

\newacronym[\glsshortpluralkey= SOA,\glslongpluralkey= SOA]{SOA}{SOA}{Special Objects Array}

\newacronym[\glsshortpluralkey= IUT,\glslongpluralkey= IUT]{IUT}{IUT}{Institut Universitaire de Technologie}


