\subsection{Integrate a research team}

Even while I  learned a lot technically, humanly I  discovered a new working environment inside the RMoD team, where communication and autonomy are really important.
\begin{itemize}
	\item The communication is the backbone of the research work whether written or oral Another member of the team was working on a similar project (\emph{PineKernel}) and each day we sent an email to the whole team with a sum up of our daily work. This way we were aware of each other work, and we shared a lot of knowledge. Moreover, I have often take a seat and ask a question to another team member, and spent hours sharing ideas and quickly test them. A large part of ideas used in Hazel were born this way, and it was really pleasant to work this way. 
	\item The autonomy in work was import too because I had to make my own schedule and to learn how to manage my time. Moreover, I was alone working on the Hazel project, so I had to set a rhythm by myself. In the other hand, I forced myself not to work at home, to keep a regular rhythm which is big change compared to the \gls{IUT}.
\end{itemize}

I also had multiple points of view on the work of a researcher, which is the job I would like to do. Moreover, the team being multi-cultural, I've learned some cultural parts from Argentinian culture (like Alfajoles), or Ukrainian one. It was really cool to practice my english with people from all over the world.

\subsection{Pharo, a living community}

Beside working for the \gls{INRIA}, I worked as a member of the active \gls{Pharo} community. I had developed some projects before being a member of the team. Those projects have been improved and integrate into the current version of \gls{Pharo}. These improvements have been done with the help of other members of the community especially during Sprints (coding session). This community is really reactive and any question, from the dumbest one to the more specific one, can be asked on the mailing list you will always have an answer.


\inanutshell It was really a good experience that I hope I could reproduce. I really like to manage a project by myself, and to schedule my work alone. Moreover I really like to work on a research theme.