I have technically learned a lot during my internship at many levels. Here is a non-exhaustive list of things I have learned or deepened.

\paragraph{Smalltalk.} I already knew \gls{Smalltalk} before the beginning of the internship. But I have improved my knowledge about the \gls{Smalltalk} language especially because I used to borrow a lot of books from the lab, in particular the ones about dynamic languages. Thanks to \gls{Smalltalk}, and the fact that you can browse living objects, I understand how an object-oriented language works more deeply.

\paragraph{Pharo.} By analyzing the \gls{Pharo} kernel then the whole system, I have read a lot of code and this way learned a lot about the \gls{Pharo} internal structure. It allows me to think at the precise definition of a kernel, which classes are needed to run a system. Thanks to these analyses, I now have a better comprehension of modular packages.

\paragraph{The Virtual Machine.} I have learned bases of how the \gls{VM} works and how to create a new version of the current \gls{VM} using \ct{VMMaker}. I have also learned how to add new primitives in the system. I really would like to know more about the \gls{VM}, because it used to looks like a black box even if the system can't work without the \gls{VM}.

\paragraph{English.} The team being multi-cultural with people from several countries, the english is used all the time for the internal communications. Moreover, all the mails shared in the Pharo mailing list are in english too. I started to learn how to write a research paper in english.

\paragraph{SVN.} The team is using \gls{SVN} for storing internal information, so I had to learn how it works.